% SPDX-FileCopyrightText: Copyright (c) 2020-2025 Yegor Bugayenko
% SPDX-License-Identifier: MIT

\cleardoublepage
\sect{Message from Organizers}

We welcome you to the third International Conference on Code Quality (ICCQ'23)!
At this turbulent time,
it was a challenging task for us
to put together an international Program Committee,
to find sponsors,
to obtain support form IEEE Computer Society,
to organize a double-blind review process,
and to prepare the Proceedings you are reading now.

We are very thankful to the Program Committee members who
reviewed all research papers submitted to us. Thanks to them,
each paper received at least three reviews and the selection of the best papers to publish
was done in an objective and fair competition. Our objective,
similar to the last year, was to make our conference high quality.
That's why our rejection ratio was very high: only the
papers with undoubtedly positive feedback from reviewers were published.

We would like to express our appreciation to all authors.
We strongly encourage them to return to us next year
with their new research results.

It's important to mention that we would not be able to make
ICCQ happen without the support of our academia partners:
St. Petersburg State University,
Innopolis University,
HSE University,
and
Bauman Moscow State Technical University.
We also thank our industry partners for their financial and media support.

We thank the IEEE Computer Society for letting us publish ICCQ proceedings
in their publishing system.

Finally, thanks to all of you as attendees and, once again, welcome to ICCQ!

\vspace{18pt}
Yegor Bugayenko\\
Org Committee Chair
