\clearpage
\sect{Message from Organizers}

We welcome you to the first International Conference on Code Quality (ICCQ'21)
and to Moscow, Russia! This is our first event and we did all we could to make
it worthwhile your attention. It was a challenging task for us:
to put together a truly international and independent Program Committee,
to find academia and industry sponsors,
to convince IEEE Computer Society to become our sponsors,
to promote the conference among researchers worldwide,
to organize double-blind review process,
and to prepare the proceedings you are reading now.

We are very thankful to Program Committee members who
reviewed 23 research papers submitted to us. Thanks to them,
each paper received at least three reviews and the selection of the best papers to publish
was done in an objective and fair competition. Our objective right
from the start was to make our conference of high quality.
That's why our rejection ratio was very high: only the
papers with undoubtfully positive feedback from reviewers were published.

We would like to express our appreciation to all authors.
We strongly encourage them to return to us next year
with their new research results.

It's important to mention that we would not be able to make
ICCQ happen without the support of our academia partners:
HSE University,
Moscow State University,
Moscow Institute of Physics and Technology,
and Ivannikov Institute for System Programming of the RAS.
We also thank our partners for their financial and media support:
Huawei, SberCloud, Yandex, and Kaspersky.
We are very thankful for our community partners: RUSSOFT and SECR.

We thank IEEE Computer Society for letting us publish ICCQ proceedings
in their publishing system.

Finally, thanks to all of you as attendees and once again, welcome to ICCQ!

Yegor Bugayenko\\
Org Team Chair
