% SPDX-FileCopyrightText: Copyright (c) 2020-2025 Yegor Bugayenko
% SPDX-License-Identifier: MIT

\clearpage
\sect{Message from Program Committee}

Dear Delegates and Colleagues,

We are very pleased to welcome you to the First International Conference on Code Quality at the HSE University in Moscow, Russia. This special conference kicks off the new series, and therefore, we hope it launches a tradition to follow, and an opportunity for a rapid spin up. This ICCQ conference was organized by the HSE and a few leading IT innovative companies such Huawei and Yandex. We are happy that the ICCQ 2021 attracted such renowned experts as \nospell{Jens Palsberg}, \nospell{Anders Møller}, and \nospell{David West}, to mention a few. The papers were submitted from the world over, and choosing the best of best was a challenge even for our lofty jury. The conference attracted speakers and attendees from the USA, Europe, and Asia; therefore, this is truly an international event.

Although ICCQ started as a relatively small single-day conference, it immediately gained the IEEE support. The plan for the next years is to embrace the world while keeping high quality standards.

We sincerely hope that the delegate number increases, and the event gradually becomes a worldwide forum for the professional R\&D community in the area of software quality. Thanks to the immense efforts of the PC members and conference organizers, this new ICCQ series will probably serve a successful launchpad for international networking, publication, and collaboration.

Let me thank the hosting HSE University, the Program Committee and the organizing team for the great job they did to give birth to this new venture. I hope to meet all of you in the next events that will bring the software quality to a much wider audience!

Thanks again,\\
Prof. Dr. Sergey V. Zykov\\
Software Engineering Department\\
Computer Science Faculty\\
HSE University\\
Moscow, Russia
