% SPDX-FileCopyrightText: Copyright (c) 2020-2025 Yegor Bugayenko
% SPDX-License-Identifier: MIT

\cleardoublepage
\sect{Message from Program Committee}

Dear conference participants,

There are many criteria used to assess software quality.
They relate to different stages of software development and maintenance.
Among this wide range of criteria, those directly connected with writing programs and checking their correctness are of particular importance.
It is at these stages that mistakes are made—mistakes that can often lead to catastrophic consequences.

By bringing together specialists in code quality, this conference provides an opportunity to discuss pressing and highly relevant issues across a broad spectrum, from formal program verification to the practical work of writing software.
Through presentations and discussions, participants can broaden their perspectives and develop new ideas for further research.
It is also worth emphasizing the significant contribution of the participants in shaping the program, which includes many new and original ideas.

I accepted with gratitude the organizers’ invitation to ICCQ and tried to offer support, to the extent possible, in preparing and holding this event.
I would also like to note the considerable work carried out by the organizing committee, which made it possible to host the conference at a high level.
I wish the participants and organizers continued creative success and the achievement of new scientific results that contribute to improving software quality.

\index{Legalov, Alexander}
\vspace{18pt}
Sincerely,\\
Prof. \nospell{Alexander Legalov}\\
HSE University \\
Chairman of the Program Committee \\
