% SPDX-FileCopyrightText: Copyright (c) 2020-2025 Yegor Bugayenko
% SPDX-License-Identifier: MIT

\cleardoublepage
\sect{Message from Organizers}

We welcome you to the fifth ICCQ conference, organized in partnership with IEEE Computer Society.

The purpose of our conference, which we intend to continue for years to come, is to connect computer scientists from the West with universities and researchers in Russia.
We aspire to position ICCQ alongside the conferences we hold in high regard, including OOPSLA, PLDI, and POPL.
We recognize that a long journey lies ahead, and we remain committed to realizing this vision despite all the challenges.

The quality of ICCQ is our foremost priority.
For us, quality means rigorous and impartial peer review.
To evaluate submissions thoroughly and select the best for publication, we rely on a professional and dedicated Program Committee.
This year, we are proud to have two ACM Fellows on our Program Committee:
  Thomas Ball from Microsoft Research
  and
  Ranjit Jhala from the University of California, San Diego.
We are grateful to all PC members for their dedicated efforts in providing thorough reviews.

We could not have organized this conference without Ural Federal University and IEEE Siberian Section, our valued and supportive partners.

Above all, the most valuable contribution came from the authors who chose ICCQ as the publication venue for their work.
We look forward to receiving their submissions at future ICCQ conferences.

\vspace{18pt}
Yegor Bugayenko\\
Org Committee Chair
