\cleardoublepage
\sect{Message from Program Committee}

Dear Conference Participants,

In the realm of software engineering and programming languages, numerous
renowned conferences are organized by prestigious universities and eminent
scientists. This prompts a pertinent question: What is the significance of yet
another conference? What value can a new, smaller, and younger conference bring
to the academic community? These questions arose when the ICCQ organizers
invited me to serve as the Chair of their Program Committee.

I firmly believe that both well-established and emerging conferences have their
rightful places in computer science. New venues, although organized following
principles established by larger events, can positively influence the
mechanisms of academic publishing. The challenges faced by their organizers are
reminiscent of those encountered by their predecessors decades ago. However,
the solutions they devise are often innovative and can be more effective.

I gladly accepted the invitation from the ICCQ organizers and have no regrets.
The quality of papers submitted to ICCQ this year was commendable. The Program
Committee members performed excellent work in reviewing the papers and
selecting the top four. The contributions of these studies to the domain of
software code quality are significant. I wish all conference organizers success
in their future research endeavors and invite them to return to ICCQ next
year.

\index{Shalyto, Anatoly}
\vspace{18pt}
Sincerely,\\
Prof. \nospell{Anatoly Shalyto}\\
ITMO University \\
Chairman of the Program Committee \\
