\cleardoublepage
\sect{Message from Organizers}

We welcome you to the fourth International Conference on Code Quality (ICCQ'24)!

If you have been following our conference, you have likely noticed that the quality of accepted papers has been increasing each year. We believe this is due to the diligent efforts of our Program Committee members in their reviews. Every paper submitted to our conference undergoes at least three blind reviews, and only those papers without a single suggestion for rejection are accepted. We plan to maintain this high standard in the coming years. This year, the acceptance rate was as low as 17\%, with only four papers accepted out of 23 submitted for review. As in previous years, our objective is not to become large, but to focus on the quality of published papers.

We are very thankful to the 26 members of the Program Committee who participated in the review process purely out of enthusiasm. We are especially thankful to the ACM Fellows who joined the Program Committee this year: Philip Wadler from the University of Edinburgh and Ranjit Jhala from the University of California.

It was an honor for us to have Xin Xia from the SEAT Lab of Huawei as a keynote speaker this year. We would like to express our appreciation to all authors and strongly encourage them to return next year with their new research results.

It is important to mention that we would not be able to make ICCQ happen without the support of our academic partners: Innopolis University, St. Petersburg State University, and HSE University.

We also thank the IEEE Computer Society for allowing us to publish ICCQ proceedings in their publishing system.

Finally, thank you to all attendees, and once again, welcome to ICCQ!

\vspace{18pt}
Yegor Bugayenko\\
Org Committee Chair
